Title Goes Here

### 2020-04-24 analysis/paper/paper.Rmd
delete some unnecessary codes

SYG6 site data and analysis

@@

# artifacts from SYG6 site: now it has two layers, two phases
library(stringr)
SYG6_df <- 
  df %>% 
  filter(str_detect(files, "SYG6"))

@@

# remove stage 1 artefact
SYG6_xx_pca <- 
SYG6_df_sitename %>% 
  filter(SPstage.Stage != 1) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

SYG6_xx_pca1 <- 
  data.frame(SYG6_xx_pca$x,
             stage = as.factor( SYG6_df_sitename$SPstage.Stage[SYG6_df_sitename$SPstage.Stage !=1]))

@@

SYG_1 site data and analysis

@@

# artifacts from SYG1 site
library(stringr)
SYG_1df <- 
  df %>% 
  filter(str_detect(files, "SYG1"))

SYG_1df_sitename <- SYG_1df %>% 
  mutate (files = str_remove_all(files, "_.tps")) %>% 
  separate (files, into = c("sitename", "files"), sep = "_") %>% 
  select (-files)

#list of all attributes without ID
SYG_1DF <- SYG_1df[,1:7]

#simpler way to calculate Correlataion, you can use
SYG_1cor <- cor(SYG_1DF)

#a scatterplot matrix of Correlation
pairs(SYG_1DF)

cplot_SYG_1 <- corrplot(SYG_1cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

# CV
map_df(SYG_1DF, cv)

SYG_1PCA <- prcomp(SYG_1DF, center = TRUE, scale = TRUE)

# remove stage 1 artefact
SYG_1xx_pca <- 
SYG_1df_sitename %>% 
  filter(SPstage.Stage != 1) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

SYG_1xx_pca1 <- 
  data.frame(SYG_1xx_pca$x,
             stage = as.factor( SYG_1df_sitename$SPstage.Stage[SYG_1df_sitename$SPstage.Stage !=1]))

#plot for both stage
SYG_1gg_stage <- 
ggplot(SYG_1xx_pca1 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

fviz_pca_var(SYG_1xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

SYG_1PC1_v <- fviz_contrib(SYG_1xx_pca, choice = "var", axes = 1, top = 7)
SYG_1PC2_v <- fviz_contrib(SYG_1xx_pca, choice = "var", axes = 2, top = 7)

grid.arrange(SYG_1PC1_v, SYG_1PC2_v, nrow =1)

>>>>

SYG6 site data and analysis: artifacts from SYG6 site: now it has two layers, but the same phase (2nd)

@@

library(stringr)
SYG6_df <- 
  df %>% 
  filter(str_detect(files, "SYG6"))

@@

# remove stage 1 artefact
SYG6_xx_pca <- 
SYG6_df_sitename %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

SYG6_xx_pca1 <- 
  data.frame(SYG6_xx_pca$x,
             stage = as.factor( SYG6_df_sitename$SPstage.Stage))

@@

SYG1 site data and analysis: artifacts from SYG1 site, which include two differnt locations(excavation pits) and the artifacts are from different phase.
SYG1_2 : 3rd phase
SYG1_1: 2nd phase

@@

library(stringr)
SYG1_2df <- 
  df %>% 
  filter(str_detect(files, "SYG1_2"))

library(dplyr)
SYG1_2df_sitename <- SYG1_2df %>% 
  mutate (files = str_remove_all(files, "_\\d+.tps")) %>% 
  rename(sitename = files)

#list of all attributes without ID
SYG1_2DF <- SYG1_2df[,1:7]

#simpler way to calculate Correlataion, you can use
SYG1_2cor <- cor(SYG1_2DF)

#a scatterplot matrix of Correlation
pairs(SYG1_2DF)

cplot_SYG1_2 <- corrplot(SYG1_2cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

# CV
map_df(SYG1_2DF, cv)

SYG1_2PCA <- prcomp(SYG1_2DF, center = TRUE, scale = TRUE)

# remove stage 1 artefact
SYG1_2xx_pca <- 
SYG1_2df_sitename %>% 
  select(-sitename, -SPstage.Stage) %>% 
  prcomp(., center = TRUE, scale = TRUE)

SYG1_2xx_pca1 <- 
  data.frame(SYG1_2xx_pca$x,
             stage = as.factor(SYG1_2df_sitename$SPstage.Stage))

#plot for both stage
SYG1_2gg_stage <- 
ggplot(SYG1_2xx_pca1 ,
       aes(PC1,
           PC2,
       colour = stage)) +
  geom_point() +
  stat_ellipse()

fviz_pca_var(SYG1_2xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

SYG1_2PC1_v <- fviz_contrib(SYG_1xx_pca, choice = "var", axes = 1, top = 7)
SYG1_2PC2_v <- fviz_contrib(SYG_1xx_pca, choice = "var", axes = 2, top = 7)

grid.arrange(SYG1_2PC1_v, SYG1_2PC2_v, nrow =1)
